---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Rmazon

The goal of Rmazon is to help you download product information and reviews from Amazon.com easily.

## Installation

You can install Rmazon from github with:

```R
# install.packages("devtools")
devtools::install_github("56north/Rmazon")
```

### Example - product information

This is a basic example which shows you how to get product information:

```{r}
# Get product information for 'The Art of R Programming: A Tour of Statistical Software Design'
product_info <- Rmazon::get_product_info("1593273843")

# Have a look at the data
product_info
```

Lets get the same information, but from the **german** Amazon
```{r}
# Find the appropriate domain
Rmazon::domains$Germany

# Then use domain to get german data
product_info_de <- Rmazon::get_product_info("1593273843", domain = "de")
```


### Example - product reviews

This is a basic example which shows you how to get reviews:

```{r}
# Get reviews for 'The Art of R Programming: A Tour of Statistical Software Design'
reviews <- Rmazon::get_reviews("1593273843")

# Have a look at the data
reviews
```

Lets get the same information, but from the **french** Amazon
```{r}
# Find the appropriate domain
Rmazon::domains$France

# Then use domain to get german data
reviews_fr <- Rmazon::get_reviews("1593273843", domain = "fr")
```

